Models pretest

### 2022-12-08 Submission/Models_pretest.Rmd
levels correct

                                            location), "Amazonian States",

@@

                                          "International", "Brasilia",
                                          "Non Amazonian States")))

@@

stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = ".001pt",
                      font.size="small",
                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
                                             "Social Development", "National Sovereignty"),
                          covariate.labels = c("Speech outside Brazil", "Speech in Brasilia", "Speech in Non-amazonian Brazilian States", "Yearly Deforestation", "Yearly Inflation", "Election Year", "Peak Year"))
```

>>>>

                                            location), "Amazonian Countries",

@@

                                          "Non Amazonian States",
                                          "Brasilia",
                                          "Amazonian Countries",
                                          "International")))

@@

stargazer::stargazer(c1, c2, c3, c4, digits = 3, no.space = TRUE,
                     title = "Fixed-effects logistic regressions by president with controls",
                      column.sep.width = ".001pt",
                      font.size="small",
                      dep.var.labels = c("Environmental Conservation", "Economic Integration",
                                             "Social Development", "National Sovereignty"),
                          covariate.labels = c("Non Amazonian States", " Brasilia", "Amazonian Countries", "International", "Yearly Deforestation", "Yearly Inflation", "Election Year", "Peak Year"))
```
